Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-07-01 analysis.Rmd
Fix smraposo.R
fixed auc - plyr rename issue
ressults csv + mods

passing <- c("mkeil","jreynolds","jmarias","jsalloum","ehermann",
              "lampinen")
failing <- c("smraposo", "auc", "rhiac", "jedtan", "salehi")

@@

>>>>

passing <- c("salehi","smraposo","jedtan","mkeil","jreynolds","jmarias","jsalloum","ehermann",
              "lampinen","auc","rhiac")
failing <- c( NA )

@@

Save.

```{r}
write_csv(all_project_info, "data/all_project_info.csv")
```

### 2016-07-01 paper/paper.Rmd
ressults csv + mods

ppt <- project_plan %>%
        select(cite, expt_num, open_data,
               open_materials, original_on_turk, original_n,collected_n)

@@

```{r}
mean(project_plan$replicated_TA)
```

```{r}
mean(project_plan$replicated_student, na.rm=TRUE)
```

@@

```{r}
project_plan %>% 
  group_by(original_on_turk) %>%
  summarise(replicated_TA = mean(replicated_TA))
```

@@

```{r}
project_plan %>% 
  group_by(fidelity) %>%
  summarise(replicated = mean(replicated_TA))
```

>>>>

results <- read_csv("data/all_project_info.csv")

d <- left_join(project_plan, results)
```

```{r}
ppt <- project_plan %>%
        select(cite, expt_num, open_data,
               open_materials, original_on_turk, original_n,collected_n)

@@

```{r}
mean(d$replicated_TA)
```

```{r}
mean(d$replicated_student, na.rm=TRUE)
```

@@

```{r}
d %>% 
  group_by(original_on_turk) %>%
  summarise(replicated_TA = mean(replicated_TA))
```

@@

```{r}
d %>% 
  group_by(fidelity) %>%
  summarise(replicated = mean(replicated_TA))
```
